In the following the systematic uncertainties which are taken into
account in the fit to the $m_{WV}$ and $m_{ZV}$ shapes are listed.  
Uncertainties which do not only influence the overall normalization
(\eg the uncertainty in the luminosity measurement), but also the
distribution of relevant kinematic observables (\eg the uncertainty in
the jet energy scale), are treated as shape uncertainties. Their
impact is evaluated by performing the full analysis not only for the
central value of the relevant parameter, but also with its value
shifted up and down by one standard deviation. For
each source of uncertainty, the impact in different bins of the final 
distribution is thus considered fully correlated, while
independent sources of uncertainty are treated as uncorrelated. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Luminosity}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The assigned uncertainty to the integrated luminosity measurement for
the data set used in this analysis is 2.5\%.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Trigger, lepton reconstruction and identification efficiencies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Discrepancies in the lepton reconstruction and identification
efficiencies between data and simulation are corrected by applying
to all MC samples 
data-to-simulation scale factors measured using $\dyll$ events in the $\cPZ$
peak region~\cite{wzxs} that are recorded with unbiased triggers. These factors
depend on the lepton \pt and $\eta$ and are within 1-2\% for electrons and muons.
The uncertainty in the determination of the trigger efficiency leads to an uncertainty smaller than 1\% in the expected signal yield. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Lepton momentum scale}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The lepton momentum scale uncertainty is computed by varying the
momentum of the leptons by their uncertainties. We have an 
uncertainty in the muons and electrons of 1\%. We follow the recommendations of the Exotica group for the high $p_{T}$ muons~\cite{Twiki:EXO-MUODocumentationRun2}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Jet energy scale and resolution}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The uncertainty in the calibration of the jet energy scale (JES) and resolution (JER) 
directly affects the acceptance of the requirement $< 2$~jets, 
the $\met$ computation, and all the cuts related to jets. 
The estimate of the jet energy scale uncertainty is performed varying 
the jet energy scale up and down by 1$\sigma$ as
measured by the Jet/MET group~\cite{twiki:JES}. The variation
corresponds to a simple re-scaling of the jet four-momentum as
follows: $P\rightarrow P \cdot (1 \pm \delta\pt^{JES}/{\pt})$, where 
$\delta\pt^{JES}$ is the absolute uncertainty on the jet energy scale
which is parametrized as function of the $\pt$ and $\eta$ of the jet. 

A similar strategy is performed to evaluate the systematic related to
the jet energy resolution. In order to reproduce in MC the jet
resolution measured in data the momentum of jets used in this 
analysis is smeared as 
%%
\begin{equation}
p_{\rm T} \rightarrow \max \left[0 , p_{T}^{\rm gen} + c_{\pm1\sigma}\cdot (p_{\rm T}-p_{\rm T}^{\rm gen}) \right]
\end{equation}
%%
in which $c_{\pm1\sigma}$ are the data-to-MC scale factors 
shifting the central value by $\pm$1$\sigma$. These values are taken 
from the official CMS recommendations for 2016~\cite{twiki:JES}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{B-tagging efficiency}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In this analysis the b-tagging is used to reject events with real b-jets in the final state since the signal events have little b-jet content. The recipe provided by the BTV group using the recommended measurements has been used to both reweight the b-tagging (in)efficiencies of the selected jets and to estimate 
the associated uncertainties.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Pileup}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

MC samples are re-weighted with 69.2 mb as MinBias cross section to reproduce the pileup conditions observed in data.
To compute the uncertainty related to this re-weighting procedure, we
shift the mean of the distribution of real interaction in MC by the
suggested value~\cite{twiki:Pileup} of 5\%. 
The variation of the final yields induced by
this procedure is about 5\% in MC estimated processes. 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{MC statistics}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

For the processes estimated from simulation,,the
available statistics of the MC sample limits the precision of the
modeling, and is therefore taken as a systematic
uncertainty. Similarly, the backgrounds estimated from data are
limited by the available statistics in the corresponding control
samples. Therefore, for these uncertainties, the same treatment is
used as in the case of MC-driven backgrounds.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Summary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

All of the systematic uncertainties on normalizations are given a log-normal 
distribution. A summary of the relative systematic uncertainties in the estimated signal and background
yields is shown in Table~\ref{tab:HwzSystematics}.
\begin{table*}[htbp]
\topcaption{Relative systematic uncertainties in the estimated signal and background yields in units of percent.\label{tab:HwzSystematics}}
  \centering
\cmsTableResize{\begin{scotch}{lccccc}

 Source & Signal & $W$+jet & $WV$  & top & $Z$+jet    \\

        \hline
Integrated luminosity      & 2.5 &  \NA  &  2.5  &   \NA  & \NA	 \\
Lepton efficiency          & 1.0  &  \NA  & 1.0  &  1.0  & \NA  \\
Jet momentum scale         & shape  & \NA &  shape  &  shape  & \NA 	 \\
Lepton momentum scale      & shape  & \NA &  shape  &  shape  & \NA 	 \\
b tagging                  & 2.0 & \NA &  2.0 &   3.0  & 2.0 	 \\
$V$ tagging                & 8.0 & \NA &  8.0 &  8.0  & \NA 	 \\
QCD scale                  & 22.0 &  \NA  &  38.0  &  \NA  & \NA 	 \\
PDF unc.                   & 6.0 & \NA &  9.0  &   \NA  & \NA	 \\
bkg. normalization         & \NA & 15.0 &  \NA  &  10.0  &  15.0 \\
$W$+jet shape              & \NA & shape & \NA & \NA & \NA \\
$Z$+jet shape              & \NA & \NA & \NA & \NA & shape \\
Jet/MET resolution         & 4.0 & \NA &  3.0  & 2.0  & \\\
Pileup modeling            & 5.0 & \NA & 4.0 & \NA & \NA \\
Limited MC stat.           & shape & \NA & shape & shape & \NA \\
      \end{scotch}}
\end{table*}
