% Acknowledgements ============================================================

%\pdfbookmark[1]{Acknowledgments}{acknowledgments}
\chapter*{Acknowledgments}
% As the saying goes, good premises do not entail good stories. 
It is a matter of immense pleasure to pen down these lines to express my sincere thanks to the people who have bestowed upon me their loving blessings and the heart pledged support because of which I am able to stand where I am today.

First, I would like to express my sincere gratitude to my PhD supervisor Dr Md. Naimuddin, for accepting me as a student. I could not have imagined having a better supervisor and mentor for my PhD study, who not only guided me for the research work but also taught me a lot about life, how to work with different people in a group/collaboration and many more.

Besides him, my sincere thanks also go to our group professors - Dr. Ashutosh Bhardwaj, Dr. Ashok Kumar, Prof. Brajesh Choudhury and Prof. Kirti Ranjan for their guidance and discussion during my PhD study. I gratefully thank Prof. Sanjay Jain, Head, Department of Physics, for allowing me to utilize facilities of the department. 

% Along with this, I would like to thank Archana Sharma, Dan Green, Jeffrey Berryhill and Aram Apyan for their helpful discussion and support during my thesis work and without whose guidance this work would not have been possible.

I would also like to thank Dr. Archana Sharma for her constant help and support throughout my Ph.D. and specifically while I involved in the muon detector-related activities. I learnt a lot from her about the work culture and how to work coherently in big collaborations like the one we have at CERN. Thank you for setting an example of how to work hard, lead and inspire. Apart from this I won't forget the Indian parties she used to organise for our colleagues from  India and Pakistan. 

I would also like to pay my sincere gratitude to Senior Scientist Jeffrey Berryhill and Emeritus Scientist Dan Green with whom I had the great opportunity to work at the Fermilab. I enjoyed working with them and learnt a lot during our  discussions. Without their help and guidance, my physics analysis work would not have been possible.

During my physics analysis, I had a great helping hand from Dr. Aram Apyan who spent a lot of his time helping me understand, learn and work on various analysis techniques, not only as a mentor but as a friend. I always like the way he used to explain things in a very efficient and simplistic manner. 

I would also like to thank INDIA-CMS collaboration for providing me with a platform to discuss my work by arranging regular Collaboration meetings. 

This research work has been carried out based on the CMS experiment at the CERN LHC, Fermilab and University of Delhi lab. My endeavour in research got boosted due to the excellent academic, cordial and conversant atmosphere prevailing in these institutions of excellence. I would like to thank the whole CMS collaboration, the scientists, and the technical and the administrative staff at the LHC accelerator complex and the CMS experiment. A special word of thanks goes to my seniors Dr Arun Kumar, Dr Ajay Gupta and Dr Varun Sharma. I am extremely grateful for their enormous support during the early stages of my PhD.

I am thankful to the lab staff Md Yunus, Amir Hussain, Sanjay and Pradhan at the University of Delhi who contributed directly or indirectly throughout this research work. I gratefully acknowledge the financial support received from DAE-DST and UGC during the entire period of my research work.

I am lucky enough to have been given the supportive gift of amazing people in my life, without all of whom, this work would not have been completed. I would like to thank my seniors and colleagues at our research laboratory at the University of Delhi - Dr Daljeet Kaur, Dr Shivali Malhotra, Geetika Jain, Sumit Keshri, Ankit Gaur, Aashiq Shah, Aman Phogat, Asar Ahmed, Mohit Gola, Priyanka Phogat, Arjun Chhetri, Prabhjot Singh, Rocky Bala Garg, Prajesh Sharma, Mohd. Rafiq, Rizwan and Hemant. I cannot express how much I have learnt and enjoyed working with all of them during the last six years. Also, I would like to thank my other friends - Ankita Mehta, Anterpreet Kaur, Ridhi Chawla and Dr Archie Sharma - from India-CMS collaboration.
I am happy to acknowledge Ankita Mehta for critically reviewing this thesis and putting her valuable suggestions which helped me a lot. 
I would also like to thank my some of the school and college friends like Sunil Pandey, Rajesh Patel, Vijay Bhatt, Ved Prakash, Dinesh Kumar Verma, Praveen Gautam, Ramesh Sharma, Nitika Mangala, Jitender, Sumit Kumar and Dheeraj Chandwani for numerous cheerful and unforgettable moments I have shared with them.

I would like to express my special thanks to Sumit Kumar for being my roommate for three years. His continuous admiration, support and trust has always helped me maintain my confidence level and given me the morale boost to overcome the hurdles of my life. You will always be the brother of my soul and the friend of my heart.

I would also like to thank my wife Archana for her immense care and helping me in thesis writing. Also, I would like to thank my brother-in-law Dr. Arvind Kumar for supporting and giving me his help during my thesis writing.

I do not have words to express my obligation and gratitude to my beloved parents, who always supported me in this journey. I very much remember with gratitude my parents, who played a big role in shaping me what I am today through their continuous counselling and suggestions. I remember the blessings and affections of all my relatives and well-wishers since my childhood with has contributed in shaping my life and career. I owe my knowledge and desire to learn more to all my respected teachers - Manju Sharma, Mani Shankar Pandey, Dr. Arijit Choudhury, Dr. Manisha Verma, Dr. Sanjeeta Gupta and Prof. Vinay Gupta - inspired me at the different stages of my life.

Last but not least, I would like to thank the most compassionate Almighty for giving me the strength, courage, ability and opportunity to undertake this research study and to accomplish it.\\[3.0cm]
Date:\\
Place: Delhi \hfill Ram Krishna Sharma
