\begin{center}
\doublespacing
{\LARGE \textbf{List of Publications}}
\end{center}
{\Large\textbf{Journal Publication:}}
\begin{enumerate}
% %{%\large
\item ``Development, characterization and qualification of first GEM foils produced in India", Aashaq Shah, Asar Ahmed, Mohit Gola, \textbf{Ram Krishna Sharma}, Shivali Malhotra, Ashok Kumar, Md. Naimuddin, Pradeep Menon, K. Srinivasan,\\``\textit{Nuclear Instruments and Methods in Physics Research Section A: Accelerators, Spectrometers, Detectors and Associated Equipment'', 892 (2018), pp. 10-17} (\textbf{Corresponding Author})

\item ``Search for anomalous electroweak production of WW/WZ/ZZ boson pairs in association wiht two jets in proton-proton collision at 13 TeV'', CMS Collaboration\\To be submitted in: \textit{Physics Letters B}
% % }
\end{enumerate}
%
\vspace{0.3cm}
%
{\Large \textbf{CMS Analysis Notes:}}
\begin{enumerate}
%{%\large 
\item ``Search for anomalous electroweak production of WW/WZ/ZZ boson pairs in association with two jets in proton-proton collision at 13 TeV'', 
Aram Apyan, Andrew Beretva, Jeffrey Berryhill, Pietro Govoni, Dan Green, Md. Naimuddin, Jakob Salfeld-Nebgen, \textbf{Ram Krishna Sharma}, Patricia Rebello Teles, Davide Valsecchi\\
{\bf CMS Analysis Note - 2017/236}.
%}
\end{enumerate}
%
\vspace{0.3cm}
{\Large \textbf{CMS Detector Notes:}}
\begin{enumerate}
%{%\large 
\item ``Test beam studies of Gas Electron Multiplier (GEM) detectors for the upgrade of CMS endcap muon system'', 
Vipin Bhatnagar, Brian Dorney, Marek Michal Gruchala, Priyanka Kumari, Ankita Mehta, Md Naimuddin, Jeremie Alexandre Merlin, Archana Sharma, \textbf{Ram Krishna Sharma}, J.B. Singh \\{\bf CMS Detector Note - 16/017}.
%}
\end{enumerate}
%
\vspace{0.3cm}
{\Large \textbf{Conference Proceedings/Poster Presentations:}}
\begin{enumerate}
	\item ``Test Beam Study of Gas Electron Multiplier (GEM) Detectors for the Upgrade of CMS Endcap Muon System'', {\textbf{Ram Krishna Sharma}}.\\
	Talk presented at the \textbf{XXII DAE High Energy Physics Symposium}, University of Delhi, India, December 12-16, 2016.\\
	\textbf{Published Proceeding:} \textbf{Ram Krishna Sharma} et al. “Test Beam Study of Gas Electron Multiplier (GEM) Detectors for the Upgrade of CMS Endcap Muon System”. In: XXII DAE High Energy Physics Symposium. Springer International Publishing, 2018, pp. 179–183. doi:10.1007/978-3-319-73171-1\_40.

	\item ``Charged particle detection performance of Gas Electron Multiplier (GEM) detectors for the upgrade of CMS endcap muon system at the CERN LHC'', \textbf{Ram Krishna Sharma}.\\
	Poster presented at the \textbf{2015 IEEE Nuclear Science Symposium and Medical Imaging Conference (NSS/MIC)}, Town and Country Hotel, San Diego, California, USA, 31 October - 7 November 2015.\\
	\textbf{Published Proceeding:} D. Abbaneo,..., \textbf{R. Sharma}, et al. “Charged particle detection performance of Gas Electron Multiplier (GEM) detectors for the upgrade of CMS endcap muon system at the CERN LHC”. 2015 IEEE Nuclear Science Symposium and Medical Imaging Conference (NSS/MIC). IEEE, 2015. doi:10.1109/nssmic.2015.7581797.

\end{enumerate}
